Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-04 submission.tex
Minor changes

The article is structured as follows. We start out by reviewing
previous work on tag set evaluation in Section \ref{sec:prev} and
\ref{sec:data} provides an overview of the treebank used for
experimentation. Section \ref{sec:setup} describes the experimental
setup used in our work and Section \ref{sec:optimization} goes on to
provide the results from our optimization experiments. Finally,
Section \ref{sec:summary} summarizes our main findings and discusses
some avenues for future work.

\section{Previous/Related work}
\label{sec:prev}
There is a considerable lack of previous efforts on extrinsic evaluation of the
effects of PoS tag sets on downstream applications. We will consider(/noe
annet, considerable...consider) papers that evaluate the effects of PoS tag
set granularity on PoS tagging. This includes investigation of the effects of
PoS tag sets on tagging of Swedish \cite{Meg:01,Meg:02} and English
\cite{Mac:05}.

>>>>

The article is structured as follows. We start out by reviewing
previous work on tag set evaluation in Section \ref{sec:prev} and
Section \ref{sec:data} provides an overview of the treebank used for
experimentation. Section \ref{sec:setup} describes the experimental
setup used in our work and Section \ref{sec:optimization} goes on to
provide the results from our optimization experiments. Finally,
Section \ref{sec:summary} summarizes our main findings and discusses
some avenues for future work.

\section{Previous/Related work}
\label{sec:prev}
There has been little previous work dedicated specifically to
extrinsic evaluation of the effects of PoS tag sets on downstream
applications.  There has, however, been some work that evaluates the
effects of PoS tag set granularity on PoS tagging. This includes
investigation of the effects of PoS tag sets on tagging of Swedish
\cite{Meg:01,Meg:02} and English \cite{Mac:05}.
